Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-05 paper/paper.tex
misc revision

Then to effectively construct the meta-continuation @new_mcont@, we define an auxiliary function
@makeMCont@, which takes a list of closures as arguments and returns the meta-continuation. 
Function @makeMCont@ is a recursive function where the recursive invocation happens when 
constructing the meta-continuation based on the rest of closures set. 
Now we can dynamically generate the meta-continuation inside of a meta-continuation.
Meanwhile, the @new_cont@ we defined above is used here, simply because of different closures 
actually share the same continuation.
The case where the empty closures set occurs is also interesting. At this case,
the outer meta-continuation @mcontinue@ is returned.
It would be clear if we inductively think the base case where the closures set contains only one 
closure, then @makeMCont@ is invoked with an empty set, therefore should be just the 
current meta-continuation @mcontinue@.

>>>>

Then to address the circularity of the meta-continuations, we define an auxiliary function
@makeMCont@ to construct @new_mcont@, which takes a list of closures as the argument and returns 
the meta-continuation. 
Function @makeMCont@ is a recursive function where the recursive invocation happens when 
constructing the meta-continuation based on the rest of closures set. 
Now we can dynamically generate the meta-continuation inside of a meta-continuation.
Meanwhile, the @new_cont@ we defined above is used here, simply because of different closures 
actually share the same continuation.
The case where the empty closures set occurs is also interesting. At this case,
the outer meta-continuation @mcontinue@ is returned.
It would be clear if we inductively think the base case where the closures set contains only one 
closure, then @makeMCont@ is invoked with an empty set, therefore should be just the 
current meta-continuation @mcontinue@.
